Coordinated monitoring of the Piney Point wastewater discharage into Tampa Bay: Data synthesis and reporting

### 2022-05-16 manu-draft.Rmd
added sampling effort table

data(demtab)
data(rsallpts)

@@

* Monitoring details - effort, agencies, methods, TBEP coordination, refer to MPB paper for details, Figure \@ref(fig:map)
* Synthesis workflow Figure \@ref(fig:synthesis)
     * Challenges - multiple streams, messy AF
     * Solutions - centralized data uploads, R tools for synthesis (import, testing, app integration)
     * Sorta unified data structure (but see metadata section)
* Repository setup - synthesis and app

@@

* Analytics and where it was linked (e.g., DEP, myfwc), not analytics did not start until May 13th, 2021
     * Average time spent on app, mobile vs desktop (go to analytics to get this)
     * Total users over time (from Google Analytics), Figure \@ref(fig:analytics)
     * Users by geographic location (country, state, city), Table \@ref(tab:demtab)

@@

* Data effort over time

>>>>

data(efftab)
data(demtab)
data(rsallpts)

@@

* Monitoring details - effort, agencies, methods, TBEP coordination, refer to MPB paper for details, Figure \@ref(fig:map), Table \@ref(tab:efftab)
* Synthesis workflow Figure \@ref(fig:synthesis)
     * Challenges - multiple streams, messy AF
     * Solutions - centralized data uploads, R tools for synthesis (import, testing, app integration)
     * Sorta unified data structure (but see metadata section)
* Repository setup - synthesis and app

@@

* Analytics and where it was linked (e.g., DEP, myfwc), note analytics did not start until May 13th, 2021
     * Average time spent on app, mobile vs desktop (go to analytics to get this)
     * Total users over time (from Google Analytics), Figure \@ref(fig:analytics)
     * Users by geographic location (country, state, city), Table \@ref(tab:demtab)

@@

```{r efftab}
cap.val <- 'Sampling effort for response-based monitoring by partners from April 1st 2021 through September.  Values show the total number of unique sites samples for water quality, algae (phytoplankton), and seagrass/macroalgae in Tampa Bay.  Values in parentheses show the percentage of the total for each monitoring type.'
knitr::kable(efftab, booktabs = T, caption = cap.val)
```
